As I conclude this work, I would like to express gratitude to some of the people that provided me with support and encouragement throughout the process of writing this thesis.\\
First, I'd like to thank Prof. Dr. Christian Holm for giving me the opportunity to write this thesis and believing in the potential of machine learning applications in a physical context. Further, I'm very grateful to my advisor M. Sc. Samuel Tovey for all the time and effort that went into giving me great advice and guidance. I also owe thanks to M. Sc. Konstantin Nikolaou for teaching me a lot about scientific research and stepping in whenever I needed further guidance. Working at the ICP was a pleasure, since all the great people there created a friendly and inspiring working environment. Here, I also want to specifically thank Julian Ho\ss bach for great talks, help whenever I needed it and a lot of design inspiration.\\\par
Additionally, I want to thank Svenja for keeping me sane, Etienne for being an incredible smorgasbord of knowledge and always being happy to share some of it, and all the other Atzen from the Fachschaft for the right amount of distractions during long working days. I'm also grateful to Tareq, for the fact that he would have always helped if I had needed him and for generally contributing a lot to the person I am today.\\\par
Finally, I need to thank my family for all the trust and support throughout all of my life - Zum Schluss möchte ich meiner Familie für die allgegenwärtige Unterstützung und das tiefe Vertrauen in meinen eigenen Lebensweg danken.